Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-07-14 doc/report/msc-report.tex
report: method chapter.

@@

TODO: ALL OF THIS.
After having become familiar with the problem and its theoretical solution, it
was time to design the software.

Our initial design was ambitious: it contained, amongst other things, a query
language and sub-components for query analyzation, to identity the most common
queries, and for query optimization. These are likely advantageous features in a
large data store but one can do without them.

In the end, we much simplified our initial design and ended up with a design
that was simpler and more to-the-point.

% TODO: method.
TODO: -- Limits on cardinality --

@@

Zohmg is designed as a data store, which simply imports, stores, and exports
data. Although presenting the data is important, this is left to the user to
solve. This restriction was made because of keeping the implementation simple,
and more general.

@@

>>>>

TODO: -- Limits on cardinality --

@@

After familiarity with the problem and its theoretical solution was reached,
the design phase was entered. During this phase a grand design for the system
was layed out.

The initial design was ambitious; it contained, amongst other things, components
to import, store, and exporte data, a query language and sub-components for
query analyzation. The intended tasks for these components were to identify the
most common queries and optimization. These features are likely advantageous in
a large data store but it is possible to do without them.

In the end, it was decided to use a simplified version of the initial design.
As mentioned in chapter 3 in the section System Components, the final design
only included components to import, store, and export data.

@@

Zohmg is designed as a data store, which simply imports, stores, and exports
data. Although presenting the data is important, this is left to the user to
solve. The section Design Phase in this chapter mentions an original plan where
a query language and sub-components for optimization were included. In the end,
these were left out. These restrictions were made because of keeping the
implementation simple, and more general.

@@

TODO: add summary on cardinality limits on cardinality here.
